Decentralised location proof system

### 2016-04-12 thesis/background.tex
Updates after proofreading Introduction and Design chapters

\section{Proving your location}
As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, we are losing the security that previously existed by requiring physical interaction between humans to transfer sensitive data

@@

\begin{figure}[H]
\resizebox {\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
\caption{Proof encrypted with group signature (Adapted from Luo et al. \cite{luo})}
\label{fig:luo_transaction}
\end{figure}

@@

\begin{itemize}
	\item[] \textbf{False presence}: A dishonest user tries to obtain a location proof for a false location.
	\item[] \textbf{Malicious intruders}: A malicious intruder offers to help another user prove a false location, but doesn't prove a false location for himself.
	\item[] \textbf{Curious users}: A curious user learns another user's identity while the user is acquiring the location proof.
	\item[] \textbf{Malicious applications}: The application that the user is proving his location to takes advantage of the user's information.
	\item[] \textbf{Eavesdroppers}: An eavesdropper intercepts or modifies communication between two honest users.
	\item[] \textbf{Wormhole attacks}: An attacker records network traffic in one location and replays it in another location (at another time).
	\item[] \textbf{Weak identities}: A user gives his public key or identity to another colluding user in order to create a location proof.
	\item[] \textbf{False timestamping (backdating, future dating)}: In a backdating attack, the attacker creates a location proof with a past timestamp. In future dating, the attacker creates a location proof with a future timestamp
	\item[] \textbf{Implication}: A malicious user, or group of colluding malicious users, create a false location proof for an honest user.
	\item[] \textbf{False assertion}: Two malicious users collude to create a false location proof for themselves.
	\item[] \textbf{Proof switching}: A malicious user modifies one of its existing honest proofs to spoof a false location.
	\item[] \textbf{Relay attack}: A malicious user creates a location proof with an honest user by relaying his requests through a colluding \textit{proxy user}, who is physically present at a location that the malicious user wishes to create false proofs at.
	\item[] \textbf{Sybil attack}: A Sybil attack occurs when a single malicious user of the system generates multiple \textit{pseudoidentities} and masquerades as multiple users \cite{sybil}.
\end{itemize}

>>>>

\section{Proving your location}
As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, we are losing the security that previously existed by requiring physical interaction between humans to transfer sensitive data.

@@

\begin{figure}[H]
\begin{center}
\resizebox {0.7\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
\caption{Proof request with group signature (Adapted from Luo et al. \cite{luo})}
\label{fig:luo_transaction}
\end{center}
\end{figure}

@@

\begin{itemize}
	\item[] \textbf{False presence}: A dishonest user tries to obtain a location proof for a false location.
	\item[] \textbf{Malicious intruders}: A malicious intruder offers to help another user prove a false location, but doesn't prove a false location for himself.
	\item[] \textbf{Curious users}: A curious user learns another user's identity by monitoring its location proofs.
	\item[] \textbf{Malicious applications}: The application that the user is proving his location to takes advantage of the user's information.
	\item[] \textbf{Eavesdroppers}: An eavesdropper intercepts or modifies communication between two honest users.
	\item[] \textbf{Wormhole attacks}: An attacker records network traffic in one location and replays it in another location (at another time).
	\item[] \textbf{Weak identities}: A user gives his public key or identity to another colluding user in order to create a location proof.
	\item[] \textbf{False timestamping (backdating, future dating)}: In a backdating attack, the attacker creates a location proof with a past timestamp. In future dating, the attacker creates a location proof with a future timestamp
	\item[] \textbf{Implication}: A malicious user, or group of colluding malicious users, create a false location proof for an honest user.
	\item[] \textbf{False assertion}: Two malicious users collude to create a false location proof for themselves.
	\item[] \textbf{Proof switching}: A malicious user modifies one of its existing honest proofs to spoof a false location.
	\item[] \textbf{Relay attack}: A malicious user creates a location proof with an honest user by relaying his requests through a colluding \textit{proxy user}, who is physically present at a location that the malicious user wishes to create false proofs at.
	\item[] \textbf{Sybil attack}: A Sybil attack occurs when a single malicious user of the system generates multiple \textit{pseudoidentities} and masquerades as multiple users \cite{sybil}.
\end{itemize}

### 2016-04-12 thesis/design.tex
Updates after proofreading Introduction and Design chapters

The location proof system I propose allows \textit{mobile nodes} to create location proofs for each other after physically meeting. When two mobile nodes are in close physical proximity, they initiate a transaction over a short range, ad-hoc network such as Bluetooth.

To create a transaction, two mobile nodes anonymously share their GPS coordinates and current time over a short-range network. Both nodes then check that these parameters don't differ by more than some value $\epsilon$. Once satisfied, they each create an encrypted, privacy-protecting transaction logging their location and the identity of the other mobile node (the \textit{alibi}) used to create the transaction. This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain} \cite{blueprint}.

Once given permission from a mobile node (by transferring decryption keys), a \textit{Verifier node} can consult the data in blockchain and determine whether or not the mobile node is present at its claimed location. The blockchain is managed by a network of \textit{Miner nodes}, who collect transactions from mobile nodes, distribute them across the network, and try to create a new \textit{block} of transactions by attempting to solve a \textit{proof-of-work} puzzle.

Any mobile node acting as an alibi in a transaction will share details of its most recent transactions with the other mobile node in the transaction. This means that when the mobile node seeks verification from a Verifier node, the Verifier can examine the mobile node's alibi's, and each of the alibi's recent alibi's, forming a large graph of connections which can be used to verify or reject the mobile nodes claimed location. Only the owner of the transaction can give permission to a Verifier to check its location history, by providing the Verifier with the keys needed to decrypt the transactions.

@@

\begin{enumerate}[label=\textbf{\arabic*}.]
\item Two mobile nodes in close physical proximity create a transaction.
\item The mobile nodes each publish their transaction to a Miner node.
\item The Miner node distributes the transaction across the Miner network.
\item One Miner node solves the proof-of-work for a block of transactions, and the new block of transactions is appended to the blockchain.
\item A mobile node requests verification from a Verifier node (request structure is explained in section \ref{ssec:verification}).
\item The Verifier node uses the public blockchain to examine the requesting node's transactions and determine their validity.
\item The Verifier accepts or rejects the  mobile node's claimed location based on its transactions in the blockchain. 
\end{enumerate}

@@

When a mobile node is created, it generates a public/private key pair. To maintain anonymity, the mobile node will use the public key to encrypt \textit{nonces} to create \textit{identities}, and use these to identify itself in a transaction. A different identity will be created for each transaction. During the verification stage, the node will provide the Verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions (see figure \ref{fig:verify_request}). This allows the Verifier to calculate all of the node's identities, and prove that they were all created by the same node, and can then retrieve the transactions associated with those identities from the blockchain. The Verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.

\subsection{Nonce list} \label{sssec:nonce_list}
A \textit{Nonce List} is simply a list of all of the nonces a mobile node has used so far to generate identities. When a mobile node generates a new identity, it must first generate a new nonce which is then encrypted to create the identity. The nonce is appended to the mobile node's nonce list, so it can be used later during verification (see section \ref{ssec:verification}).

\subsection{Identity duplication}
Since all identities are generated from random nonces, there is nothing to stop two nodes from generating the same identity and using it in different transactions. It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID in the blockchain. The Verifier will have a decryption key for the transaction it is searching for, which will only be able to decrypt one of the transactions with the duplicate ID. The Verifier will try to decrypt each one until it finds one that can be decrypted successfully.

\newpage
\section{Transactions} \label{sec:transactions}
During a transaction between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes an honest, successful transaction, assuming an ad-hoc Bluetooth network has already been set up between nodes $A$ and $B$.

\begin{figure}[H]
\resizebox {\columnwidth} {!} {\input{diagrams/transaction.tex}}
\caption{Honest, successful transaction}
\label{fig:transaction}
\end{figure}

\begin{itemize}
	\item[] \textbf{(1)} Before the transaction begins, both nodes generate a new entry in their nonce list, and generate a new identity from that nonce.
	\item[] \textbf{(2)} Node A sends its identity to Node B, along with its observed current timestamp $ts_A$ and current GPS location $loc_A$.
	\item[] \textbf{(3)} Node B verifies that the observed timestamp and GPS location received from Node A are within an acceptable difference from its own observations. This difference is defined by some system constant $\epsilon$.
	\item[] \textbf{(4)} If Node B verifies the parameters received from Node A, it will respond with its own identity and observations for A to verify.
	\item[] \textbf{(5)} Node A verifies that the parameters received from B differ by no more than $\epsilon$ from its own observed parameters.
	\item[] \textbf{(6)} Node A sends $KP_{An}$, its $nth$ \textit{Key Packet}. Key Packets are used to provide alibi credibility, and are discussed in section \ref{sssec:key_packets}.
	\item[] \textbf{(7)} B responds with its own Key Packet.
	\item[] \textbf{(8)} Both nodes generate their own transaction $T$, using their alibi's Key Packets. These are then published onto the public blockchain.
\end{itemize}

Where:
\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{NL_A[n]}$ is the $n$th nonce in $A$'s \textit{Nonce List}, which is used to generate $ID_{An}$ (see section \ref{sssec:nonce_list}).
\end{itemize}

\null
When a node is initialised, it must begin to record two \textit{Key Lists} for itself. A \textit{Key List} is a list of encryption keys previously used for transactions. For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively. These \textit{Key Lists} and are assumed to have been initialised and populated before the transaction described in Figure \ref{fig:transaction} begins.

After creating an ad-hoc Bluetooth network between nodes $A$ and $B$, the first step in the transaction is for both nodes to share their IDs, and agree upon a GPS location and current time. Nodes likely won't share the exact same GPS coordinates or time, but once the values don't differ by more than some small constant $\epsilon$, the nodes will continue with the transaction. If node $A$ claims a GPS location or timestamp that differs from what node $B$ senses by more than $\epsilon$, node $B$ will abort the transaction.

After nodes agree upon the parameters of the transaction, they exchange their previous ID, along with their \textit{Key Packets}. A \textit{Key Packet} is a list of keys used in a node's $n$ most recent transactions, along with the transaction ID's if necessary. This allows node $A$ to decrypt node $B$'s $m$ most recent transactions, therefore providing an alibi for node $A$.

\subsection{Transaction creation}
Once nodes have exchanged \textit{Key Packets}, their communication is finished and they can close their ad-hoc channel. Each node creates a new transaction object, $T$, to publish onto the public blockchain. The following transaction data will be calculated by node $A$, after communicating with node $B$:
\\

$T_{An} = KL_{AT}[n](ts|loc|ID_{An}|ID_{Bm}|KP_{Bm})$
\\

Where:
\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.	
	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
	\item[] $\mathbf{ID_{An}}$ is $A$'s $nth$ identity, used for this transaction only.
	\item[] $\mathbf{ID_{Bm}}$ is $B$'s $mth$ identity.
	\item[] $\mathbf{KP_{Bm}}$ is $B$'s \textit{Key Packet} at time $m$. Its exact contents are discussed in more detail in section \ref{sssec:key_packets}
\end{itemize}

@@

\textit{Backwards-chaining} is an important part of verifiability. The Verifier must be able to prove that the proof chain provided by the mobile node has not been chronologically re-ordered. The transaction must therefore be accompanied by a link to the node's chronologically previous transaction. This link must be encrypted, along with the transaction timestamp, to prevent a curious user from monitoring the public blockchain to observe a user's transaction publishing activity. $A$'s copy of the transaction log $P_{An}$ will therefore be in the form:
\\

$P_{An} = ID_{An}|KL_{AL}[n](ID_{An-1}|ts_A)|T_{An}$

\null
To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well. The transaction will then be signed into the next block in the blockchain.

@@

\null
In this case, $KL_{BT}[m-1]$ has not been included with $KL_{BL}[m-1]$, in order to protect the privacy of this transaction. This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created withing 5km of his home, in order to protect his privacy.

@@

To abort the transaction, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain. This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present. Any transaction on the blockchain that do not contain a reference to a valid  alibi transaction will be disregarded during verification.

\begin{figure}[h]
\resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
\caption{An aborted transaction due to malicious node $M$}
\label{fig:aborted_transaction}
\end{figure}

\section{Verification} \label{ssec:verification}
\begin{minipage}{0.5\linewidth}
In the verification stage, a mobile node tries to prove its location to a Verifier node, e.g. a bank. To do this, the mobile node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}:
\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{ID_{An-1}}$ is the ID of $A$'s most recently published transaction.
	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet up to transaction $n-1$, and includes keys for as many transactions as $A$ feels is appropriate in order to receive verification.
	\item[] $\mathbf{loc}$ is $A$'s current claimed GPS coordinates for which it is seeking verification.
	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a subset of its \textit{Nonce List} (section \ref{sssec:nonce_list}). A Nonce Packet is the list of the nonces used to generate $A$'s most recent IDs, up to $n-1$., that $A$ is willing to share with the Verifier. 
\end{itemize}
\end{minipage}
\hfill
\begin{minipage}[c]{0.5\linewidth}
\begin{figure}[H]
\input{diagrams/verify_request.tex}
\caption{Verification request}
\label{fig:verify_request}
\end{figure}
\end{minipage}

The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming. Given $ID_{An-1}$ and $KP_{An-1}$, a Verifier is able to retrieve $A$'s previous transactions, and the transactions of all of its alibi's.

@@

There are a huge number of possible factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain Verifiers, and kept secret to improve reliability and avoid gaming. Some simple example factors may include:
\begin{itemize}
	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the Verifier will reject his verification request.
	\item \textbf{Alibi reuse:} if the Verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
	\begin{itemize}
		\item Due to transaction anonymity, the Verifier may not always be able to tell if two alibi's are the same person or not. e.g. node $A$ could use node $B$ as an alibi, then wait for $B$ to complete $n$ more transactions, then use node $B$ again.
		\item This is not a viable attack on the verification system. Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
	\end{itemize}
\end{itemize}

>>>>

The location proof system I propose allows \textit{mobile nodes} to create location proofs by initiating an \textit{exchange} with another anonymous mobile node. When two mobile nodes are in close physical proximity, they initiate an exchange in the background over a short range, ad-hoc network such as Bluetooth. On completion of the exchange, both nodes can generate their own \textit{transaction}, a cryptographically secure proof of location, attested by the other mobile node.

To create a transaction, two mobile nodes anonymously exchange their GPS coordinates and current time over the ad-hoc network. Both nodes then check that these parameters don't differ from their own observed parameters by more than some value $\epsilon$. Once satisfied, they each create an encrypted, privacy-protecting transaction logging their location and the identity of the other mobile node (the \textit{alibi}) used to create the transaction. This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain} \cite{blueprint}. Once given permission from a mobile node, a \textit{Verifier node} can consult the data in blockchain and determine whether or not the mobile node is present at its claimed location.

Any mobile node acting as an alibi in a transaction will share details of its most recent transactions with the other mobile node in the exchange. This means that when the mobile node seeks verification from a Verifier node, the Verifier can examine the mobile node's alibi's, and each of the alibi's recent alibi's, forming a large tree of connections which can be used to verify or reject the mobile nodes claimed location. Only the owner of the transaction can give permission to a Verifier to check its location history, by providing the Verifier with the keys needed to decrypt the transactions.

@@

\begin{enumerate}[label=\textbf{\arabic*}.]
\item Two mobile nodes come in close physical proximity and create an ad-hoc network, over which they initiate an exchange and each create a transaction.
\item Both mobile nodes publish their own transaction to a Miner node.
\item The Miner node who received the transaction distributes it across the Miner network.
\item One Miner node solves the proof-of-work for a block of transactions, and the new block is appended to the blockchain.
\item A mobile node requests verification from a Verifier node (request structure is explained in section \ref{ssec:verification}).
\item The Verifier node uses the public blockchain to examine the requesting node's transactions and determine their validity.
\item The Verifier accepts or rejects the  mobile node's claimed location based on its analysis of the transactions in the blockchain. 
\end{enumerate}

@@

When a mobile node is first joins the network, it generates a public/private key pair. To maintain anonymity, the mobile node will use the public key to encrypt \textit{nonces} to create \textit{identities}, and use these to identify itself in a transaction. A different identity will be created for each transaction. During the verification stage, the node will provide the Verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions (see figure \ref{fig:verify_request}). This allows the Verifier to calculate all of the node's identities, and prove that they were all created by the same node. The Verifier can then retrieve the transactions associated with those identities from the blockchain. The Verifier will also ensure that the node owns the private key associated with the provided public key, to prevent a weak identity attack.

\subsection{Nonce list} \label{sssec:nonce_list}
A \textit{Nonce List} is simply a list of all of the nonces a mobile node has used so far to generate identities. When a mobile node wishes to generate a new identity, it must first generate a new nonce which is then encrypted to create the identity. The nonce is appended to the mobile node's nonce list, so it can be used later during verification (see section \ref{ssec:verification}).

\begin{figure}[H]
\resizebox {\columnwidth} {!} {\input{diagrams/nonce_list.tex}}
\caption{Identity generation from Nonce List}
\label{fig:nonce_list}
\end{figure}

In figure \ref{fig:nonce_list} above, nonce $0047$ is encrypted with $K^+$ to create identity $ee3bc14$. By providing the nonce list and $K^+$, a node can prove that it created all of the identities in the identities list. It must also verify that it owns $K^-$, its private key.

\subsection{Identity duplication}
Since all identities are generated from random nonces, there is nothing to prevent two nodes from generating the same identity and using it in different transactions. It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID while searching the blockchain. The Verifier will have a decryption key for the transaction it is searching for, which will only successfully decrypt one of the transactions with the duplicate ID. The Verifier will try to decrypt each one until it finds the one that can be decrypted successfully.

\newpage
\section{Transactions} \label{sec:transactions}
During an exchange between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes and explains an honest, successful exchange, assuming an ad-hoc Bluetooth network has already been set up between nodes $A$ and $B$.

\begin{figure}[H]
\begin{center}
\resizebox {1.1\columnwidth} {!} {\input{diagrams/transaction.tex}}
\caption{Honest, successful exchange}
\label{fig:transaction}
\end{center}
\end{figure}

\begin{itemize}
	\item[] \textbf{(1)} Before the exchange begins, both nodes generate a new entry in their nonce list (e.g. $NL_A[n]$), and generate a new identity from that nonce (e.g. $ID_A[n]$).
	\item[] \textbf{(2)} Node A sends its identity to Node B, along with its observed current timestamp $ts_A$ and current GPS location $loc_A$.
	\item[] \textbf{(3)} Node B verifies that the observed timestamp and GPS location received from Node A are within an acceptable difference from its own observations. This difference is defined by some system constant $\epsilon$.
	\item[] \textbf{(4)} If Node B verifies the parameters received from Node A, it will respond with its own identity and observations for A to verify.
	\item[] \textbf{(5)} Node A verifies that the parameters received from B differ by no more than $\epsilon$ from its own observed parameters.
	\item[] \textbf{(6)} Node A sends $KP_{An}$, its $nth$ \textit{Key Packet}. Key Packets are used to provide alibi credibility, and are discussed in section \ref{sssec:key_packets}.
	\item[] \textbf{(7)} B responds with its own Key Packet.
	\item[] \textbf{(8)} Both nodes generate their own transaction $T$, using their alibi's Key Packets. These are then used to generate $P$, the data published onto the public blockchain.
\end{itemize}

\subsection{Key Lists}
When a node is initialised, it must begin to record two \textit{Key Lists} for itself. A \textit{Key List} is a list of encryption keys previously used for transactions. For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively. These \textit{Key Lists} and are assumed to have been initialised and populated before the transaction described in Figure \ref{fig:transaction} begins.

\subsection{Transaction creation}
Once nodes have exchanged \textit{Key Packets}, their communication is finished and they can close their ad-hoc channel. Each node creates a new transaction, $T$, and generates data $P$ to publish onto the public blockchain. The following transaction will be created by node $A$, after communicating with node $B$:
\\

$T_{An} = KL_{AT}[n](ts|loc|ID_{A}[n]|ID_{B}[m]|KP_{Bm})$
\\

Where:
\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
	\item[] $\mathbf{KL_{AT}}$ is $A$'s transaction \textit{Key Lists}, used to encrypt transactions.	
	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
	\item[] $\mathbf{ID_{A}[n]}$ is $A$'s $nth$ identity, used for this transaction only.
	\item[] $\mathbf{ID_{B}[m]}$ is $B$'s $mth$ identity.
	\item[] $\mathbf{KP_{Bm}}$ is $B$'s \textit{Key Packet} at time $m$. Its exact contents are discussed in more detail in section \ref{sssec:key_packets}
\end{itemize}

@@

\textit{Backwards-chaining} is an important part of verifiability. The Verifier must be able to prove that the proof chain provided by the mobile node has not been chronologically re-ordered. This is the ``order preserving'' property of OTIT \cite{otit}. The transaction must therefore be accompanied by a link to the node's chronologically previous transaction. This link is encrypted with $KL_{AL}[n]$, $A$'s $nth$ \textit{link} key list, to prevent a curious user from monitoring the public blockchain to observe a user's transaction publishing activity. The timestamp $ts_A$ is also included in the backwards-chaining data, to verify the ``order preserving'' property. $A$'s transaction data $P_{An}$ will therefore be in the form:
\\

$P_{An} = ID_{An}|KL_{AL}[n](ID_{A}[n-1]|ts_A)|T_{An}$

\null
To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well. The transaction will signed into the next block in the blockchain, once the next proof-of-work is solved.

Node $B$, $A$'s alibi for the above transaction example, will publish $P_{Bm}$ after the exchange. If $B$'s transaction is not available on the blockchain, $A$'s transaction will be considered invalid and disregarded during verification. A transaction $T_A$ in the blockchain must be accompanied by a reference to some valid alibi transaction $T_B$, and $T_B$ must reference $T_A$, otherwise the proof is not considered credible by a verifier.

@@

\null
In this case, $KL_{BT}[m-1]$ has not been included with $KL_{BL}[m-1]$, in order to protect the privacy of this transaction. This means that a node who received this key packet will not be able to decrypt $B$'s transaction $T_{Bm-1}$, but can still prove that a transaction exists at that time and in the correct sequence, as $B$ will still provide $KL_{BL}[m-1]$. This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created within 5km of his home, in order to protect his privacy.

@@

To abort the transaction, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain. This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present, so the transaction will be disregarded by any verifiers.

\begin{figure}
\resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
\caption{An aborted transaction due to malicious node $M$}
\label{fig:aborted_transaction}
\end{figure}

\clearpage
\section{Verification} \label{ssec:verification}
In the verification stage, a mobile node tries to prove its location to a Verifier node, e.g. a bank. To do this, the mobile node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}.

\begin{figure}[H]
\begin{center}
\resizebox {0.8\columnwidth} {!} {\input{diagrams/verify_request.tex}}
\caption{Verification request}
\label{fig:verify_request}
\end{center}
\end{figure}

\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{ID_{A}[n-1]}$ is the ID of $A$'s most recently published transaction.
	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet up to transaction $n-1$, and includes keys for as many transactions as $A$ feels is appropriate in order to receive verification.
	\item[] $\mathbf{loc}$ is $A$'s current claimed GPS coordinates for which it is seeking verification.
	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a subset of its \textit{Nonce List} (section \ref{sssec:nonce_list}). A Nonce Packet is the list of the nonces used to generate $A$'s most recent IDs, up to $n-1$, that $A$ is willing to share with the Verifier. 
\end{itemize}

\null
The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming. Given $ID_{A}[n-1]$ and $KP_{An-1}$, a Verifier is able to retrieve $A$'s previous transactions, and the transactions of all of its alibi's. This will allow the Verifier to recursively inspect the transactions of all alibi's used in a nodes transactions, until it is satisfied that the location can be verified or rejected. This recursive inspection can be visualised as a tree, as shown in figure \ref{fig:tree}.

\begin{figure}[H]
\begin{center}
\resizebox {0.7\columnwidth} {!} {\input{diagrams/tree.tex}}
\caption{Alibi chain relationship tree}
\label{fig:tree}
\end{center}
\end{figure}

In this figure, the red chain is the requesting node's transaction chain. The blue chains are the red node's alibis' transaction chains, and the black chains are the blue node's alibis' transaction chains. If the verifier wishes to recurse more, it could inspect the black node's alibis' transaction chains. Note that this is a simple example, and $n = 3$, the length of the transaction chain subset provided for verification. In reality $n$ should be much larger.

@@

There are a huge number of possible factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain Verifiers, and kept secret to improve reliability and avoid gaming. Some simple example factors may include:
\begin{itemize}
	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, they won't be considered credible alibis, and the Verifier will reject his verification request.
	\item \textbf{Transaction relevance:} if the Verifier considers the transactions it receives to be out of date, they will be rejected on the grounds that they are no longer relevant.
	\item \textbf{Alibi reuse:} if the Verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
	\begin{itemize}
		\item Due to transaction anonymity, the Verifier may not always be able to tell if two alibi's are the same person or not. e.g. node $A$ could use node $B$ as an alibi, then wait for $B$ to complete $n$ more transactions, then use node $B$ again.
		\item This is not a viable attack on the verification system. Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
	\end{itemize}
\end{itemize}

### 2016-04-12 thesis/introduction.tex
Updates after proofreading Introduction and Design chapters

>>>>

\section{Report outline}
This report consists of four additional chapters, listed biefly below.

\subsection{Background}
Chapter 2 begins with a brief introduction to the problem space. A brief explanation of decentralised and distributed networks, as well as the blockchain is then presented, in the context of location proof systems. The chapter closes with an explanation of the design goals defined for this project.

\subsection{Design}
Chapter 3 explains the design of the decentralised location proof system in detail. It begins with an overview of the entire system, and then details the design of each specific part.

\subsection{Evaluation}
Chapter 4 presents an evaluation of the system described in the design, with respect to the goals laid out in Chapter 3.

\subsection{Future work}
Chapter 5 presents the conclusions of the project, and details interesting areas for possible future work relating to the project.
